Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-05-06 ms.tex
I use the included bibliography file instead of the master one on my computer.
I added some points about the cost of only getting one DHS spectrum and also explained that the subarray sizes could theoretically be different between long wavelength and short wavelengths.

Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}). This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).

The balance between saturating the long-wavelength grism and getting enough SNR in the DHS is listed in Table \ref{tab:SatSNRsubA}. The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the DHS noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration and binned to a resolution of 100. We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} and we consider 80\% well depth in the second read as saturation. The sub-array sizes and order of DHS elements is shown in Figure \ref{fig:DHSaps}.

@@

\bibliographystyle{apj}
\bibliography{/Users/everettschlawin/evmemo_folder/pdfs/master_bib_file/master_biblio.bib}
%\bibliography{master_biblio.bib}

>>>>

Each NIRCam array must be read out with identical window sizes and exposure times due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}). The window sizes could theoretically be different between the long-wavelength and short-wavelength detectors with only software changes, but would require large changes to the existing software. This means that some balance must be made between saturating the grism spectrum (which has much higher throughput) in the long-wavelength and getting the most flux in the short-wavelength DHS spectra (which have lower throughput and also spread the light over more pixels).

The balance between saturating the long-wavelength grism and getting enough SNR in the DHS is listed in Table \ref{tab:SatSNRsubA}. The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the DHS noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration and binned to a resolution of 100. We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} and we consider 80\% well depth in the second read as saturation. The sub-array sizes and order of DHS elements is shown in Figure \ref{fig:DHSaps}. For the brightest sources, which require the 2048 $\times$ 64 pixel subarray, the DHS throughput loss is significant, because only 1 DHS spectrum out of 10 is used, meaning only about 4\% of JWST's 25 m$^2$ collecting area is used.

@@

\bibliographystyle{apj}
\bibliography{dhs_biblio}
